|

### 2021-12-15 07-Chp-Triangulation.Rmd
End of day:

In epidemiology, triangulation is the practice of using multiple sources of evidence to provide more reliable answers to a research question. Different sources of evidence will have different limitations. If the result from each source points towards the same answer, this improves our confidence in the conclusion. Triangulation can either be _qualitative_ or _quantitative_. In qualitative triangulation, the results of each evidence source are discussed. In contrast, quantitative triangulation aims to combine the different results mathematically to obtain one single overall result.

@@

In this chapter, I describe a new approach for quantitative triangulation, which combines two existing methods. For each source of evidence, I assess and account for robustness (do we believe the result, based on the methods/results of the study?) and relevance (does the source provide useful evidence relevant to the question we are interested in?). To showcase the new method, I apply it to two questions of interest. In each case, evidence from each of the previous chapters is combined to give an overall result.

@@

When combined in the new framework, the results produced by previous chapters did not support an effect of low-density lipoprotein cholesterol (LDL-c) on Alzheimer's disease nor an effect of triglycerides on vascular dementia. I close the chapter by suggesting future work to further develop the new methods presented.

>>>>

Sources of evidence often contain limitations which reduce our confidence in their results. To minimise the impact of these limitations, a method has been developed called triangulation which looks at multiple sources addressing the same question. If the result from each source points towards the same answer, this improves our confidence in the conclusion.

@@

In this chapter, I describe a new approach for triangulation, which combines two existing methods. This approach is used to ensure that the results meet the following criteria:

*	robustness - do we believe the result, based on the methods/results of the study?
*	relevance - does the source provide useful evidence relevant to the question we are interested in?

This triangulation approach is quantitative in nature, meaning I have tried to combine the results from different sources mathematically to obtain one single overall result. I have applied this method to assess the following relationships of interest:

*	the effect of midlife LDL-c on Alsheimer’s disease
*	the effect of midlife triglycerides on vascular dementia

@@

My method did not support the existence of an effect in either relationship of interest. I close the chapter by suggesting future work to further develop and improve upon the new method presented.

### 2021-12-15 front-and-back-matter/_acknowledgements.Rmd
End of day:

There are many people without whose input and support this work would have been severely diminised:

@@

Thanks must also go to those who contributed their time and energy to my research projects: Matthew Lee, Lena Schmidt, Alexandra McAleenan, and Vincent Cheng. Francesca Spiga kindly shared an advance copy of her review of tools to assess Mendelian randomisation studies, and Rebecca Turner shared her code for bias-/indirectness-adjusted meta-analyses that underpins the quantitative triangulation framework presented in Chapter \@ref(tri-heading).

A particular thank you to Emily Hennessy, with whom I co-wrote the guidance paper for preparing primary research for incorporation into systematic reviews. Similarly, thanks to Athena Sheppard for her support in assessing the impact of journal polices on open-data sharing.

>>>>

There are many people without whose input and support this work would have been severely diminished:

@@

Thanks must also go to those who contributed their time and energy to my research projects: Athena Sheppard, Emily Hennessy, Matthew Lee, Lena Schmidt, Alexandra McAleenan, Vincent Cheng, Francesca Spiga, Sarah Dawson and Rebecca Turner.
